\myTitle

### 2024-07-05 extras/Renaming-amplicons/Amplicon-renaming.Rmd
Add genomic locations plot to the supplement

```{r}
# get the chromosome numbers (pulled from NCBI page at https://www.ncbi.nlm.nih.gov/datasets/genome/GCF_018296145.1/)
chroms <- read_tsv("Otsh_v2.0_chroms.tsv") %>%
  mutate(Otsh_v2.0_chromosome = str_replace(Chromosome, "LG", ""), .before = Chromosome) %>%
  select(RefSeq, Otsh_v2.0_chromosome)

@@

>>>>

```{r}
# get the chromosome numbers (pulled from NCBI page at https://www.ncbi.nlm.nih.gov/datasets/genome/GCF_018296145.1/)
chroms0 <- read_tsv("Otsh_v2.0_chroms.tsv") %>%
  mutate(Otsh_v2.0_chromosome = str_replace(Chromosome, "LG", ""), .before = Chromosome) %>%
  select(RefSeq, Otsh_v2.0_chromosome, `Size (bp)`)

chroms <- chroms0 %>%
  select(RefSeq, Otsh_v2.0_chromosome)

@@

Before I go on, I am going to write out the Otsh_v2.0 chromosome lenghts for later use.
```{r}
chroms0 %>%
  rename(
    num_bases = `Size (bp)`,
    chrom = Otsh_v2.0_chromosome
  ) %>%
  write_tsv("Otsh_v2.0_chrom_lengths.tsv")

### 2024-07-05 tex/supplemental-figures.tex
Add genomic locations plot to the supplement

>>>>

%%%%%%%%%%%%%%%%%%%%%% 
\begin{figure}
\begin{center}
\includegraphics[width=0.7\textwidth]{images/genomic-locations-plot.pdf}
\end{center}
\caption[Genomic locations of amplicons]{\footnotesize Genomic locations of amplicons in the
Otsh\_v2.0 assembly of the Chinook salmon genome.  Color shows type of marker (see main text).
The sex-ID marker is not included here because it aligns to a scaffold that is not part of a
named chromosome/linkage group in the assembly.}
\label{fig:num-alle}
\end{figure}
%%%%%%%%%%%%%%%%%%%%
